---
title: "help"
author: "Aurelien Chateigner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{help}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This vignette exists as help is limited by CRAN to 5 seconds runs, and it
depends a lot on user's connection. It will also explain the advance use of the
package.

# Using `anyLib`

## Loading the package

To load `anyLib`, simply :
```{r loading anyLib}
library(anyLib)
```

For the purpose of the demonstration, installations in this vignette are done
in a dummy library:
```{r dummy folder}
lib <- normalizePath(tempdir(), "/")
f1 <- paste(lib, "folder1", sep = "/")
dir.create(f1)
.libPaths(f1)
```

```{r save packages, include=FALSE}
foo <- .packages()
```


The package requires `devtools` `withr` and `BiocInstaller` so to install them:
```{r installation of the dependencies}
utils::chooseCRANmirror(graphics = FALSE, 1)
install.packages("devtools")
library(devtools)
source("https://bioconductor.org/biocLite.R")
biocLite(ask = FALSE, suppressAutoUpdate = TRUE)
```

## Install and load 1 package

### CRAN package

So, if one wants to install a simple CRAN package and load it, simply:

```{r install and load a simple CRAN package}
anyLib("apercu")
```

### Bioconductor package

For a source package:
```{r install a load a source package}
anyLib(system.file("dummyPackage_0.1.0.tar.gz", package = "anyLib"),
       source = TRUE)
```


For a Bioconductor package:

```{r install and load a simple Bioconductor package}
anyLib("limma")
```

### github package

And for github, to install, one needs the name in the format
"maintainerName/packageName":
```{r install and load a simple github package}
anyLib("achateigner/dummyPackage", force = TRUE)
```

But to load it once installed, one only needs its name:
```{r only load a github package}
anyLib("dummyPackage")
```

## Install and load a list of packages

```{r reload, include=FALSE}
bar <- .packages()
foobar <- setdiff(bar, foo)
toRemove <- paste0("package:", foobar)
for (i in seq_along(foobar)) {           
    detach(toRemove[i], character.only = TRUE)    
}
```


To install and load a list of packages, from various places, with the names. I
install them in a different folder:
```{r install and load from various places}
f2 <- paste(lib, "folder2", sep = "/")
dir.create(f2)
anyLib(list("apercu", "limma", "achateigner/dummyPackage"), lib = f2,
       loadLib = f2)
```

To install and load from a list of packages in an object:
```{r reload2, include=FALSE}
bar <- .packages()
foobar <- setdiff(bar, foo)
toRemove <- paste0("package:", foobar)
for (i in seq_along(foobar)) {           
    detach(toRemove[i], character.only = TRUE)    
}
```

```{r install and load from list}
f3 <- paste(lib, "folder3", sep = "/")
dir.create(f3)
packagesNeeded <- list("apercu", "limma", "achateigner/dummyPackage")
anyLib(packagesNeeded, lib = f3, loadLib = f3)
```

## Advanced options

If one wants to reinstall a package or force the update (`force = TRUE`), not
update the Bioconductor packages (`autoUpdate = FALSE`), install in a different
lib and load from a set of libs:
```{r reload3, include=FALSE}
bar <- .packages()
foobar <- setdiff(bar, foo)
toRemove <- paste0("package:", foobar)
for (i in seq_along(foobar)) {           
    detach(toRemove[i], character.only = TRUE)    
}
```

```{r advanced options}
f4 <- paste(lib, "folder4", sep = "/")
dir.create(f4)
anyLib(packagesNeeded,
       force = TRUE,
       autoUpdate = FALSE,
       lib = f4,
       loadLib = c(f1, f4))

```
